Will Kamala Harris will win the 2024 Presidential election

### 2024-11-04 paper/paper.qmd
.

There are several limitations and weaknesses that could have affected out research and statistical analysis. First, the variable `numeric_grade` which is the variable that weighs pollster results for accuracy could have been used to determing the how we look at each pollster to make sure the pollster we chose was the most accurate of the most available, and could have included it in our model to increase accuracy of our predictions.Second, as the data from polls change often especially leading up to the election it is difficult to make realtime adjustments as new data becomes available. Next, Harris only announced her candidacy at the end of July, we did not have a very large time frame to take into account whenn looking at her polling data, as often presidential candidates begin campaigning much earlier than just a few months before the election. Further, As we only created a Model for Harris and not Trump we had less to compare to, while we believe our results would not have changed significantly it would have ben halpful to consider a model based around Donald Trump. Lastly, in recent history elections have been rather close whether they were close in electoral votes or in the popular vote, pollster are hesitant to state that one candidate will win over another even if their research and data shows otherwise as they are afraid to lose their credibility for future elections if they turn out to be wrong or if their analysis is different than the actual results.

>>>>

There are several limitations and weaknesses that could have affected out research and statistical analysis. First, the variable `numeric_grade` which is the variable that weighs pollster results for accuracy could have been used to determing the how we look at each pollster to make sure the pollster we chose was the most accurate of the most available, and could have included it in our model to increase accuracy of our predictions.Second, as the data from polls change often especially leading up to the election it is difficult to make realtime adjustments as new data becomes available. Next, Harris only announced her candidacy at the end of July, we did not have a very large time frame to take into account whenn looking at her polling data, as often presidential candidates begin campaigning much earlier than just a few months before the election. Furthermore, As we only created a Model for Harris and not Trump we had less to compare to, while we believe our results would not have changed significantly it would have been helpful to consider a model based around Donald Trump. Additionally we could have looked at the states recent voting history for their members of congress, both the senate , and the house of representatives, as well as the current political party holding power in the state, i.e. the party that the governer of each state is affiliated with. Lastly, in recent history elections have been rather close whether they were close in electoral votes or in the popular vote, pollster are hesitant to state that one candidate will win over another even if their research and data shows otherwise as they are afraid to lose their credibility for future elections if they turn out to be wrong or if their analysis is different than the actual results.
